Out-of-Sample Comparisons of Overfit Models

### 2014-03-25 paper.tex
References: Add reference for TikZ and PGF
Conflicts:
	paper.tex

This section presents two simulations that investigate the accuracy of
our theory in small samples.%
\footnote{Simulations were conducted in R \citep{Rde:10} using Sweave
  \citep{Lei:02} and the Lattice \citep{Sar:10}, RSQLite
  \citep{Jam:10}, and tikzDevice \citep{ShB:11:0.6.1} packages.} %
The first looks at the asymptotic normality of the DMW statistic
centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
section's results imply that centering on the first should give an
approximately normal statistic and centering on the second should give
a normal statistic when $P$ is small relative to $T$.  The second
simulation looks at the size and power of several statistics when
conducting inference about the difference in the models'
generalization error.  For all of the simulations, we look at
fixed-window OOS tests to speed up computation time.

@@

Both sets of simulations support our theoretical results.  The first
simulation confirms that the DMW OOS $t$-test is centered at $\E_R
\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
only when $P$ is small.  The second simulation confirms that the DMW
test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
when $P$ is small and that tests designed to test whether the
benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
and McCracken's (2007) OOS tests can reject by much more than their
nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
these simulations demonstrate that the restriction $P^2/T \to 0$ is
binding in practice, as the DMW test under-rejects and has very low
power when it is not satisfied.
\section{Empirical exercise}\label{sec:empirics}
This section presents an analysis of equity premium predictability
similar to \citet{GoW:08}.%
\footnote{All of the calculations in this
  section are done in R \citep{Rde:10}.  We also use code provided by
  \citet{Zeh:02}, \citet{Zei:04}, \citet{Har:10}, and
  \citet{ShB:11:0.6.1}.} %
We estimate the expected forecasting
performance of the largest model they consider, a model with 13
regressors, using 81 observations (annual data from 1928 to 2009).  We
construct confidence intervals for the difference in performance
between this model and a prevailing mean benchmark, and do so for
different values of $R$ and $P$ to examine the effect of the training
and test sample choice on this OOS statistic.  We find that the
estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
benchmark as $R$ increases, but it is never smaller than the
benchmark's.  This result, combined with the larger model's in-sample
significance, suggests that there may be a real relationship between
the equity premium and some of these predictors, but that the
relationship can not be estimated accurately enough to be useful for
forecasting and supports \citepos{GoW:08} conclusions.  These results
hold even when imposing \citepos{CaT:08} restriction that the equity
premium forecast be non-negative.

>>>>

This section presents two simulations that investigate the accuracy of
our theory in small samples.%
\footnote{Simulations were conducted in R \citep{Rde:10} using the
  MASS \citep{VeR:02}, Matrix \citep{BM:13}, rlecuyer \citep{SR:12},
  and RSQLite \citep{Jam:10} packages. Graphs were produced in R using
  Lattice \citep{Sar:10} and tikzDevice \citep{ShB:11:0.6.1} as well
  as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
The first looks at the asymptotic normality of the DMW statistic
centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
section's results imply that centering on the first should give an
approximately normal statistic and centering on the second should give
a normal statistic when $P$ is small relative to $T$.  The second
simulation looks at the size and power of several statistics when
conducting inference about the difference in the models'
generalization error.  For all of the simulations, we look at
fixed-window OOS tests to speed up computation time.

@@

Both sets of simulations support our theoretical results.  The first
simulation confirms that the DMW OOS $t$-test is centered at $\E_R
\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
only when $P$ is small.  The second simulation confirms that the DMW
test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
when $P$ is small and that tests designed to test whether the
benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
and McCracken's (2007) OOS tests can reject by much more than their
nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
these simulations demonstrate that the restriction $P^2/T \to 0$ is
binding in practice, as the DMW test under-rejects and has very low
power when it is not satisfied.

\section{Empirical analysis of equity premium predictability}
\label{sec:empirics}

This section presents an analysis of equity premium predictability
similar to \citet{GoW:08}.%
\footnote{Calculations in this section are done in R \citep{Rde:10}
  using the lmtest \citep{ZeH:02} and sandwich \citep{Zei:04}
  packages. Tables and grapsh were prepared with the Hmsic
  \citep{Har:10} and tikzDevice \citep{ShB:11:0.6.1} R packages as
  well as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
We estimate the expected forecasting
performance of the largest model they consider, a model with 13
regressors, using 81 observations (annual data from 1928 to 2009).  We
construct confidence intervals for the difference in performance
between this model and a prevailing mean benchmark, and do so for
different values of $R$ and $P$ to examine the effect of the training
and test sample choice on this OOS statistic.  We find that the
estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
benchmark as $R$ increases, but it is never smaller than the
benchmark's.  This result, combined with the larger model's in-sample
significance, suggests that there may be a real relationship between
the equity premium and some of these predictors, but that the
relationship can not be estimated accurately enough to be useful for
forecasting and supports \citepos{GoW:08} conclusions.  These results
hold even when imposing \citepos{CaT:08} restriction that the equity
premium forecast be non-negative.
